Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2014-01-08 paper/main.tex
minor modifications in tables

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$++$ & all masses\hMsun\\
&   & & 
wall & $--$ & all masses\\\hline

{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

@@

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &none & $<10^{12}$\hMsun\\

@@

{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &none & $<10^{12}$\hMsun\\

@@

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$-$ & $>10^{12}$\hMsun\\

@@

\cite{Trowland2013} & Hessian density & $2-5\hMpc$ & 
filament & $-$ & $> 5\times 10^{12}$\hMsun\\
&   & & 
filament & $+$ & $< 5\times 10^{12}$\hMsun\\\hline

\cite{Codis2012} & Morse Theory \& Tidal Web & $1-5\hMpc$ & 
filament & $--$ & $>10^{12}$\hMsun \\

@@

\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
filament & $++$ & only if anticorrelated with shape\\

& &  & 
filament & $--$ & only if correlated with shape\\\hline

@@

\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & filament & $-$& none\\

& &  $2.1$\hMpc &
wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline

>>>>

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$++$ & all masses\hMsun\\
&   & & 
wall & $--$ & all masses\\\hline

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

@@

\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale& Along &
Alignment & Mass dependence\\
 & & ($\hMpc$)& & & \\\hline

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ & 
filament &none & $<10^{12}$\hMsun\\

@@

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ & 
filament &none & $<10^{12}$\hMsun\\

@@

\cite{Libeskind2013} & V-Web & $1$ & 
filament &$-$ & $>10^{12}$\hMsun\\

@@

\cite{Trowland2013} & Hessian density & $2-5$ & 
filament & $-$ & $> 5\times 10^{12}$\hMsun\\
&   & & 
filament & $+$ & $< 5\times 10^{12}$\hMsun\\\hline

\cite{Codis2012} & Morse Theory \& T-Web & $1-5$ & 
filament & $--$ & $>10^{12}$\hMsun \\

@@

\cite{Zhang2009}  & Hessian density &  $2.1$ & 
filament & $++$ & if anticorrelated with shape\\

& &  & 
filament & $--$ & if correlated with shape\\\hline

\cite{AragonCalvo2007} & Hessian density & - &
wall & $++$ & $>10^{12}$\hMsun\\

@@

\cite{Hahn2007} & Tidal Web & $2.1$ & filament & $-$& none\\

& &  $2.1$\hMpc &
wall & $++$ & stronger $>10^{12}$\\\hline \hline
